The truncated KdV framework for modeling anomalous waves induced by abrupt depth changes

### 2019-07-21 paper2_JNLS/paper.tex
NM

	As discussed in \cite{bolles2019anomalous}, the experiments consist of a long, narrow wave tank (6 m long x 20 cm wide x 30 cm high), with waves generated by plexiglass paddle at one end. The waves propagate through the tank and, roughly midway through, pass over an abrupt depth change (ADC), which is created by a plexiglass step. The waves continue to propagate through the shallower depth until reaching the far end of the tank, at which point their energy is dissipated by a horse-hair dampener. Since this dampener minimizes the backscatter, the waves propagate primarily in one direction only, from left to right in Fig.~\ref{fig1}. The free surface is illuminated by light-emitting diodes that run along the bottom of the tank and imaged from the sideview with a Nikon D3300 at 60 frames per second. This arrangement allows measurements of surface displacements with a precision of 1/3 millimeter.

>>>>

	As discussed in \cite{bolles2019anomalous}, the experiments consist of a long, narrow wave tank (6 m long x 20 cm wide x 30 cm high), with waves generated by plexiglass paddle at one end. The waves propagate through the tank and, roughly midway through, pass over an abrupt depth change (ADC), which is created by a plexiglass step. The waves continue to propagate through the shallower depth until reaching the far end of the tank, at which point their energy is dissipated by a horse-hair dampener. Since this dampener minimizes the backscatter, the waves propagate primarily in one direction only, from left to right in Fig.~\ref{fig1}. The free surface is illuminated by light-emitting diodes running along the bottom of the tank and then imaged from the sideview with a Nikon D3300 at 60 frames per second. The illumination technique coupled with high pixel count of the camera allows the surface displacement to be resolved with a accuracy better than 1/3 millimeter.
